Tables

### 2018-03-20 code/tables.rmd
Removed Fisher's r-to-z from heterogeneity table
Just adjust for bias, so would be incorrect to have it in

    fit <-rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #Fisher's r-to-z transformed correlation coefficient
    fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation

>>>>

    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation

    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
    I2_2 <- rep(NA, 3) #No unstandardized version

    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))
